---
title: "Card Game"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction
Welcome to the Card Game project! In this project, you will create a simple card game using R and R Markdown. The game will involve drawing cards from a deck and comparing their values.
## Getting Started
1. Create a new R Markdown document in RStudio.
2. Name the document "Card_Game.Rmd".
3. Set the output format to HTML.
4. Write your code and explanations in the R Markdown document.
5. Knit the document to generate an HTML report.
## Project Instructions
1. Create a deck of cards with values ranging from 1 to 10.
2. Shuffle the deck of cards.
3. Draw two cards from the shuffled deck.
4. Compare the values of the drawn cards.
5. Determine the winner based on the comparison.
6. Display the winner in the R Markdown document.
$$
\sum_{i=1}^n i^2 = \frac{n(n+1)(2n+1)}{6}
$$

# Create and shuffle deck of cards
deck <- sample(1:10, replace = FALSE)  # Create deck with numbers 1-10 and shuffle without replacement
```{r error= TRUE}
deck <- sample(1:10)

# Draw cards
card1 <- deck[1]
card2 <- deck[2]

# Compare and determine winner
result <- if(card1 > card2) {
  "Player 1 wins!"
} else if(card2 > card1) {
  "Player 2 wins!"
} else {
  "Tie!
}

# Print results
print(paste("Card 1:", card1))
print(paste("Card 2:", card2))
print(result)
```